Unifying intraspecific and interspecific variation in tropical tree mortality

### 2017-06-16 ms/supp.Rnw
Add authors

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{James S Camac}
\author[a]{Mark Westoby}
\author[b]{S Joseph Wright}
\author[c]{Daniel S Falster}

\affil[a]{Department of Biological Sciences, Macquarie University NSW 2109, Australia}
\affil[b]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[c]{Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Science, University of New South Wales}

>>>>

\author[a,b,1]{James S Camac}
\author[c]{Richard Condit}
\author[d]{Richard G FitzJohn}
\author[e]{Lachlan McCalman}
\author[e]{Daniel Steinberg}
\author[a]{Mark Westoby}
\author[f]{S Joseph Wright}
\author[a,g]{Daniel S Falster}

\affil[a]{Department of Biological Sciences, Macquarie University, New South Wales, Australia}
\affil[b]{Current Address: Centre of Excellence for Biosecurity Risk Analysis, School of Biological Sciences, The University of Melbourne, Victoria, Australia}
\affil[c]{Field Museum of Natural History and Morton Arboretum, Chicago, Illinois, USA}
\affil[d]{Imperial College, London, United Kingdom}
\affil[e]{Data61, CSIRO, Australia}
\affil[f]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[g]{Current Address: Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Science, University of New South Wales, NSW 2052, Australia}
